### 2015-07-21 Harris_2015/manuscript-materials/draft.Rmd
new analyses

\noindent  
***Simulations.***
In order to compare different methods, I simulated two sets of landscapes using known
parameters.

@@

I also simulated a second set of landscapes with five, ten, or twenty
potentially-interacting species on landscapes composed of 20, 100, 500, or
2500 observed communities (24 replicate simulations for each combination; Appendix B).
These simulated data sets span the range from small, single-observer data
sets to large collaborative efforts such as the North American Breeding Bird
Survey. As described in Appendix B, I randomly drew the "true" coefficient
values for each replicate so that most species pairs interacted negligibly, a
few pairs interacted very strongly, and competition was three times more
common than facilitation. I then used Gibbs sampling to randomly generate
replicate landscapes with varying numbers of species and sites (Appendix B).
For half of the simulated landscapes, I treated each
species' $\alpha$ coefficient as a constant, as described above. For the other
half, I treated the $\alpha$ coefficients as linear functions of two abiotic
environmental factors that varied from location to location across the
landscape (Appendix B). The latter set of simulated landscapes provide an
important test of the methods' ability to distinguish co-occurrence patterns
that were generated from pairwise biotic interactions from
those that were generated by external forces like abiotic environmental
filtering. This task was made especially difficult because---as with most
analyses of presence-absence data for co-occurrence patterns---the inference
procedure did not have access to any information about the environmental or
spatial variables that helped shape the landscape [cf @connor_checkered_2013;
@blois_framework_2014].

>>>>

\noindent  
***Simulated landscapes.***
In order to compare different methods, I simulated two sets of landscapes using known
parameters.

@@

I also simulated a second set of landscapes using a stochastic community
model based on generalized Lotka-Volterra dynamics, as described in the
Appendix. In these simulations, each species pair was randomly assigned to
either compete for a portion of the available carrying capacity (negative
interaction) or to act as mutualists (positive interaction).  In these
simulations, mutualism operated by mitigating the effects of intraspecific
competition on each partner's death rate.  For these analyses, I simulated
50 replicate landscapes, each with 25, 200, or 1600 sites and 20 species.
